---
title: "MiriamAguirre"
output: html_document
date: "2024-05-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
df <- read.csv("US Project Data.csv")
```


```{r}
ggplot(df, aes(x=P_Obesity, fill = Obesity_Prob)) + 
  geom_histogram(binwidth = 1, color="black") + 
  geom_vline(aes(xintercept=median(P_Obesity)), color="darkblue", linetype="dashed",  linewidth=1) + 
  labs(x="Percentage of Obesity per County", y = "Count") + 
  theme_bw()
```

```{r}
library(ggplot2)

ggplot(df, aes(x=P_Obesity, color = Obesity_Prob)) + 
  geom_histogram(binwidth = 1, color="black", fill = "lightblue") + 
  geom_vline(aes(xintercept=median(P_Obesity)), color="darkblue", linetype="dashed",  linewidth=1) + 
  labs(x="Percentage of Obesity per County", y = "Count") + 
  theme_bw()

ggplot(df, aes(x=MedianIncE, fill = Obesity_Prob)) + 
  geom_histogram(binwidth = 5000, color="black") + 
  labs(x="Median Income per County", y = "Count") + 
  geom_vline(aes(xintercept=median(MedianIncE)), color="darkblue", linetype="dashed",  linewidth=1) + 
  theme_bw()

ggplot(df, aes(x=P_HS, fill = Obesity_Prob)) + 
  geom_histogram(binwidth = 5, color="black") + 
  labs(x="Percentage of people with a H.S. degree or higher per County", y = "Count") +
  geom_vline(aes(xintercept=median(P_HS)), color="darkblue", linetype="dashed",  linewidth=1) + 
  theme_bw()

ggplot(df, aes(x=P_FastFood, fill = Obesity_Prob)) + 
  geom_histogram(binwidth = 5, color="black") + 
  labs(x="Percentage of restaurants that are limited-service per County", y = "Count") +
  geom_vline(aes(xintercept=median(P_FastFood)), color="darkblue", linetype="dashed",  linewidth=1) + 
  theme_bw()

ggplot(df, aes(x=P_Doctor, fill = Obesity_Prob)) + 
  geom_histogram(binwidth = 5, color="black") + 
  labs(x="Percentage of adults with doctors per County", y = "Count") + 
  geom_vline(aes(xintercept=median(P_Doctor)), color="darkblue", linetype="dashed",  linewidth=1) +
  theme_bw()
```


```{r}
par(mfrow=c(2,3))
boxplot(df$P_Obesity, main = "Obesity by County", horizontal = T)
boxplot(df$MedianIncE, main = "Median Income per County", horizontal = T)
boxplot(df$P_HS, main = "High School Graduates per County", horizontal = T)
boxplot(df$P_FastFood, main = "Fast Food Restaurants per County", horizontal = T)
boxplot(df$P_Doctor, main = "Doctor Coverage per County", horizontal = T)
```



```{r}
library(GGally)

ggpairs(df[,5:9])
```


```{r}
vars <- df[,5:9]

library(corrplot)

corrplot(cor(vars),
  method = "number",
  bg="lightgray",
  outline = T,
  type = "upper" # show only upper side
)
```

```{r}
corrplot(cor(vars),
  method = "ellipse",
  outline = TRUE,
  type = "upper" # show only upper side
)
```



```{r}
library(correlation)
vars <- df[,5:9]
correlation::correlation(vars,
  include_factors = TRUE, method = "auto"
)
```

Proportion of obesity is negatively correlated with median income; counties with lower median incomes tend to have higher obesity rates. 
Proportion of obesity is negatively correlated with proportion of adults with high school education or higher; counties with lower proportion of educated adults tend to have higher obesity rates. 
Proportion of obesity is positively correlated with proportion of fast food restaurants; counties with a greater density of fast food restaurants tend to have higher obesity rates. 
There seems to be no linear relationship between proportion of obesity and proportion of doctors in a county. 

Median income and proportion of high school graduates is positively correlated. 
Median income and proportion of fast food restaurants is weakly negatively correlated; counties with higher median incomes tend to have fewer fast food restaurants.
There seems to be no linear relationship between median income and proportion of doctors. 

Proportion of high school graduates and proportion of fast food restaurants is negatively correlated; counties with a higher density of fast food chains tends to have lower high school graduate rates. 
Proportion of high school graduates and proportion of doctor coverage are positively correlated; counties with a higher proportion of high school graduates tend to have a higher proportion of doctor coverage. 

Proportion of fast food restaurants and proportion of doctor coverage is weakly negatively correlated; counties with a higher proportion of fast food restaurants tend to have a lower proportion of doctor coverage. 

Observing these correlations is important to see what patterns are in our data. 
