---
title: "Data Acquisition Code"
author: "Duy Nguyen"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidycensus)
library(tidyverse)
library(ggplot2)
library(flextable)
library(miscTools)
library(tigris)
library(gridExtra)
```

## US Census Data (This code WILL fail to run without an API key)
It is required to have an API key loaded into the package to be able to run any `get_acs()` code.
Advised to not try to run this code unless if your tidycensus is set up already.

```{r, eval = TRUE, results=FALSE}
Inc = get_acs(geography = "county",
              year = 2019, 
              variables = c(medianinc = "B19013_001"),
              survey = "acs5",
              output = "wide",
              geometry = TRUE) # Geometry was originally set to false to create the finalized data

Inc$GEOID = as.numeric(Inc$GEOID)
```

## Policymap Data:

```{r, eval = TRUE}
# Loading all PolicyMap Stuff
USObesity = read.csv("US OBESITY Percent.csv")
USEdu = read.csv("US High School Fixed.csv")
USHealth = read.csv("Doctor Access US Percent.csv")
USRestaurant = read.csv("US Restaurants Percent.csv")
```

```{r, eval = TRUE}
# Joining on the Geography code GEOID
Final_User = Inc %>% left_join(USObesity, by = c("GEOID" = "GeoID")) %>% left_join(USEdu, by = c("GEOID" = "GeoID")) %>% left_join(USHealth, by = c("GEOID" = "GeoID")) %>% left_join(USRestaurant, by = c("GEOID" = "GeoID")) %>% select(GEOID, NAME, SitsinState.x, p_crd_obesity, medianincE, phsp, pfood_fastfoodtakeout, p_doctor)
```

## Removing all NAS

```{r, eval = TRUE}
Final_User = Final_User %>% filter(phsp != "N/A" & p_crd_obesity != "N/A" & pfood_fastfoodtakeout != "N/A" & p_doctor != "N/A") # Geometry Data cannot be exported as CSV
# Use geometry for internal usage only or save it as a shape file
```

# Formatting for Use
```{r, eval = TRUE}
colnames(Final_User) = c("GeoID", "County_State", "State", "P_Obesity", "MedianIncE", "P_HS", "P_FastFood", "P_Doctor", "geometry")

Final_User$P_Obesity = as.numeric(Final_User$P_Obesity)
Final_User$P_HS = as.numeric(Final_User$P_HS)
Final_User$P_FastFood = as.numeric(Final_User$P_FastFood)
Final_User$P_Doctor = as.numeric(Final_User$P_Doctor)
```

# Adding new Classification

```{r}
Final_User = Final_User %>% mutate(Obesity_Prob = ifelse(P_Obesity > median(P_Obesity), "Higher Severity", "Lower Severity"))
```

DO NOT RUN THIS PART IT WILL CHANGE THE CURRENT CSV
```{r, eval = FALSE}
# DO NOT RUN IT WILL REPLACE THE ORIGINAL DATA (ONLY USE IF NEED UPDATE)
write.csv(Final_User, "/Users/dnguyen/Desktop/Classes/STA141C/Proj/US Project Data.csv")
```

# Visualization Section

*Loading Finalized Data:*
```{r}
Final_Simple = read.csv("US Project Data.csv")
library(tmap)
```

```{r}
ggplot(data = Final_Simple, aes(x = P_Obesity, fill = "red")) + geom_histogram(bins = 30) + theme(legend.position = "none") + labs(x = "Obesity Percentage", y = "Count", title = "Distribution of Percentage of the County with Obesity")
```

# Boxplots

```{r}
plot1 = ggplot(data = Final_Simple, aes(x = Obesity_Prob, y = MedianIncE, fill = Obesity_Prob)) + geom_boxplot() + coord_flip() + labs(title = "Median Income", y = "", x = "") + theme(legend.position = "none")
```

```{r}
plot2 = ggplot(data = Final_Simple, aes(x = Obesity_Prob, y = P_HS, fill = Obesity_Prob)) + geom_boxplot() + coord_flip() + labs(title = "High School Minimum", y = "", x = "") + theme(legend.position = "none")

```

```{r}
plot3 = ggplot(data = Final_Simple, aes(x = Obesity_Prob, y = P_Doctor, fill = Obesity_Prob)) + geom_boxplot() + coord_flip() + labs(title = "Doctor Coverage", y = "", x = "") + theme(legend.position = "none")
```

```{r}
plot4 = ggplot(data = Final_Simple, aes(x = Obesity_Prob, y = P_FastFood, fill = Obesity_Prob)) + geom_boxplot() + coord_flip() + labs(title = "Fastfood & Takeout", y = "", x = "") + theme(legend.position = "none")
```

```{r}
grid.arrange(plot1, plot2, plot3, plot4, ncol = 2)
```

# Full Map, Removed N/A in Obesity
This uses the Census API under the argument that `geography = TRUE`. It cannot run because of the tidycensus requiring an API key to get the required data.

Advised to not try to run this code unless if your tidycensus is set up already.

```{r}
Map = Inc %>% left_join(USObesity, by = c("GEOID" = "GeoID")) %>% select(p_crd_obesity, SitsinState)
Map_Filtered = Map %>% filter(SitsinState != "AK" & SitsinState != "HI" & p_crd_obesity != "N/A")
Map_Filtered$p_crd_obesity = as.numeric(Map_Filtered$p_crd_obesity)
tm_shape(Map_Filtered) + 
  tm_polygons(col = "p_crd_obesity", style = "quantile", palette = "Reds", title = "") + 
  tm_layout(
  main.title = "Percentage of Counties' Population with Obesity (Excluding Alaska & Hawaii)", 
            main.title.size = 0.9, 
            main.title.position = "center", 
            legend.outside = FALSE, 
            frame = FALSE) + 
    tm_scale_bar(text.size  = 0.5,  position = c("right", "TOP")) + 
    tm_compass(type = "4star", position = c("right", "bottom"))
```

# Map after filtering every single N/A across all variables.

```{r}
Final_Filtered = Final_User %>% filter(State != "AK" & State != "HI")
tm_shape(Final_Filtered) + tm_polygons(col = "P_Obesity", style = "quantile", palette = "Reds", title = "") + tm_layout(
  main.title = "Percentage of Counties' Population with Obesity (Excluding Alaska & Hawaii)", 
            main.title.size = 0.9, 
            main.title.position = "center", 
            legend.outside = FALSE, 
            frame = FALSE) + 
  tm_scale_bar(text.size  = 0.5,  position = c("right", "TOP")) + 
    tm_compass(type = "4star", position = c("right", "bottom"))
```





# Flextable Test

```{r}
sample_t = head(Final_Simple) %>% flextable() 
sample_t = add_footer_lines(sample_t, "Note: Geography Data not Included")
save_as_image(sample_t, path = "sample_img.png")
```

```{r}
sample_t
```

```{r}
High_Sev = Final_Simple %>% select(-County_State, -State, -GeoID) %>% filter(Obesity_Prob == "Higher Severity")

Low_Sev = Final_Simple %>% select(-County_State, -State, -GeoID) %>% filter(Obesity_Prob == "Lower Severity")

Summary = data.frame(High_Severity = colMedians(High_Sev[, c(-1, -7)]), Low_Severity = colMedians(Low_Sev[, c(-1, -7)])) %>% rownames_to_column()

Summary$rowname = c("Obesity", "Estimated Median Income", "High School Diploma", "Fastfood & Takeout", "Doctor Coverage")

Summary = Summary %>% flextable()
```

```{r}
Summary %>% set_header_labels(rowname = "Data Types", High_Severity = "High Severity", Low_Severity = "Low Severity")
```


Note:

Census Inc: 2019
Obesity: 2019 Crude Percentage
Doctor: 2018 Percentage of Doctor Coverage
High School: Percentage of High School Diploma Minimum in 2013-2017.
FastFood: 2019 Percentage